---
title: "Causal_analysis"
author: "Johannes Fuest"
date: "12/2/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
library(DOS2)
library(RItools)
library(optmatch)
library(plyr)
library(rcbalance)
library(dplyr)
```

# Read data
Here we simply read data and do some simple preprocessing. Some notes:
- Having both own and opp ptsperposs in causes multicollinearity (corr .99) -> keep only own
- Keeping StartPossScoreDiff, StartTmScore, and StartOppScore not possible due to multicollinearity -> keep only StartPossScorediff
- Remove Period due to unseen levels in factor
```{r outcome regression}
df1 <- read.csv('data_with_to_info.csv')
names(df1)[names(df1) == "def_rating"] <- "def_rating_old"
names(df1)[names(df1) == "TimeBins"] <- "TimeBins_old"
df2 <- read.csv('poss_summary.csv')
df1 <- merge(df1, df2[c("GameID", "def_rating", "Possession", "TimeBins")], by = c("GameID", "Possession"), all.x = TRUE)
df1$def_rating_old <- NULL
df1$TimeBins_old <- NULL
df1$HomeTeamTimeout <- NULL
df1 <- na.omit(df1)

columns_to_keep <- c("TimeBins","StartEvent","PossTeamWin","TimeoutCalledInitially",
                     "StartPossTime", "StartPossScoreDiff","StartTmPtsPerPoss","HomePoss","IsPlayoffs",
                     "SecondsSinceLastTimeout","ScoreDiffLastMinute", 
                     "off_rating", "def_rating", "TimeoutRemaining")

df1 <- df1[,columns_to_keep]
numeric_cols <- sapply(df1, is.numeric)
# df1[numeric_cols] <- scale(df1[numeric_cols])
df1 <- df1[!duplicated(df1), ]

# removing poss time <3
df1 <- df1[df1$StartPossTime>=3,]
df1$TimeBins <- cut(df1$StartPossTime, breaks = c(3,8,24), include.lowest = TRUE)
```

# Diff in Means
Calling a timeout appears to have a marginally positive effect, but there is 
only a .3% difference in means. It looks like not much is going on at the global level
```{r}
print(mean(df1[df1$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df1[df1$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
```

Next, we split up by bins of seconds left, which is known to make an enormous 
difference and repeat our calculation. We split into time bins from [3,8] and (8,24] seconds.
Here we can already see that the effect can change direction based on seconds left
```{r}
df_3to8 <- df1[df1$TimeBins == '[3,8]',]
df_8to24 <- df1[df1$TimeBins != '[3,8]',]
print("Diff in means for time bin [3,8] seconds")
print(mean(df_3to8[df_3to8$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_3to8[df_3to8$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print("Diff in means for time bin (8,24] seconds")
print(mean(df_8to24[df_8to24$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_8to24[df_8to24$TimeoutCalledInitially == FALSE, ]$PossTeamWin))

```

Next, we split the bins further with start event, which is known to make an enormous 
difference and repeat our calculation. The start event buckets are: 
- "Live Ball Turnover"
- "Drb" (Defensive Rebound)
- "Dead Ball Turnover"

With the exception of possessions with more than 12 seconds remaining, we see that
the sign of diff-in-means changes depending on event.
```{r}
#resetting row names here so it doesn't mess with matching later
df_3to8_live <- df_3to8[df_3to8$StartEvent == "Live Ball Turnover",]
rownames(df_3to8_live)<- NULL
df_3to8_drb <- df_3to8[df_3to8$StartEvent == "Drb",]
rownames(df_3to8_drb)<- NULL
df_3to8_dead <- df_3to8[df_3to8$StartEvent != "Live Ball Turnover" & df_3to8$StartEvent != "Drb" ,]
rownames(df_3to8_dead)<- NULL
df_8to24_live <- df_8to24[df_8to24$StartEvent == "Live Ball Turnover",]
rownames(df_8to24_live)<- NULL
df_8to24_drb <- df_8to24[df_8to24$StartEvent == "Drb",]
rownames(df_8to24_drb)<- NULL
df_8to24_dead <- df_8to24[df_8to24$StartEvent != "Live Ball Turnover" & df_8to24$StartEvent != "Drb" ,]
rownames(df_8to24_dead)<- NULL

print("Diff in means for time bin [3,8] seconds, live ball turnover: ")
print(mean(df_3to8_live[df_3to8_live$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_3to8_live[df_3to8_live$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print("Diff in means for time bin [3,8] seconds, drb: ")
print(mean(df_3to8_drb[df_3to8_drb$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_3to8_drb[df_3to8_drb$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print("Diff in means for time bin [3,8] seconds, dead ball turnover: ")
print(mean(df_3to8[df_3to8$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_3to8[df_3to8$TimeoutCalledInitially == FALSE, ]$PossTeamWin))

print("Diff in means for time bin (8,24] seconds, live ball turnover: ")
print(mean(df_8to24_live[df_8to24_live$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_8to24_live[df_8to24_live$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print("Diff in means for time bin (8,24] seconds, drb: ")
print(mean(df_8to24_drb[df_8to24_drb$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_8to24_drb[df_8to24_drb$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print("Diff in means for time bin (8,24] seconds, dead ball turnover: ")
print(mean(df_8to24_dead[df_8to24_dead$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_8to24_dead[df_8to24_dead$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
```


With these meta_variables in place, we can now begin estimating the true treatment effect of the timeout
call holding constant our covariates. We will do this by using AIPW:
1.) Esimate propensity scores using logistic regression. We will keep meta
variables in model. We use the full dataset because using the sub datasets leads to convergence issues.
```{r}
# Use only TimeoutRemaining == TRUE data for propensity score estimation
df_timeouts <- df1[df1$TimeoutRemaining == TRUE,]
# not using starting scores and per minute scores to avoid multicollinearity (was getting N/A coef values)
e_x <- glm(TimeoutCalledInitially ~ 1+StartPossTime+StartPossScoreDiff
           +StartTmPtsPerPoss+HomePoss+IsPlayoffs+SecondsSinceLastTimeout
           +ScoreDiffLastMinute+off_rating+def_rating,
             data = df_timeouts, family = binomial)
summary(e_x)
logLik(e_x)
```

2.) Estimate outcome variable with random forest for each df
```{r}
# missing
df_list <- list(df_3to8_live,df_3to8_drb, df_3to8_dead, df_8to24_live, df_8to24_drb, df_8to24_dead)
model_list <- list()
e_x_list <- list()

# set up cv for RF
  seeds <- vector("list", length = 6)
for (j in 1:5) {
  seeds[[j]] <- c(1,2,3)
}
seeds[[6]] <- c(1,2,3,4,5)
  
  # rfControl <- trainControl(method = "cv", number = 5, seeds=seeds)
 rfControl <- trainControl(method = "none")

# Loop through each DataFrame and fit a logistic regression model on treatments and controls respectively (have to leave out starting event, also leaving out period due to issues from rare overtimes)
for (i in 1:length(df_list)) {
  model_1 <-  train(as.factor(PossTeamWin) ~ 1+StartPossTime+StartPossScoreDiff+StartTmPtsPerPoss
                 +HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute
                 +off_rating+def_rating, df_list[[i]][df_list[[i]]$TimeoutCalledInitially==TRUE,], family = binomial, method = "rf", trControl = rfControl)
  
  model_0 <-  train(as.factor(PossTeamWin) ~ 1+StartPossTime+StartPossScoreDiff+StartTmPtsPerPoss
                 +HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute
                 +off_rating+def_rating, df_list[[i]][df_list[[i]]$TimeoutCalledInitially==FALSE,], family = binomial, method = "rf", trControl = rfControl)
  
e_x_temp <- glm(TimeoutCalledInitially ~ 1+StartPossTime+StartPossScoreDiff
           +StartTmPtsPerPoss+HomePoss+IsPlayoffs+SecondsSinceLastTimeout
           +ScoreDiffLastMinute+off_rating+def_rating,
             data = df_list[[i]][df_list[[i]]$TimeoutRemaining==TRUE,], family = binomial)
  
  model_list[[i]] <- list(model_1, model_0)
  e_x_list[[i]] <- e_x_temp
}
# log lik of separate prop scores
log_lik_sum = 0
for(i in 1:length(df_list)){
  log_lik_sum = log_lik_sum + logLik(e_x_list[[i]])
}
print(log_lik_sum)
```
3.) Estimate $$\hat{\mu}^{adj}$$
```{r}
tau_aipws <- list()
for (i in 1:length(df_list)) {
  df_temp <- df_list[[i]]
  mu_hat_1 <- mean((df_temp$TimeoutCalledInitially * (df_temp$PossTeamWin - (predict(model_list[[i]][[1]], newdata=df_temp, type='prob')[,2]))/predict(e_x, df_temp, type = "response")) +  (predict(model_list[[i]][[1]], newdata=df_temp, type='prob')[,2]))
  mu_hat_0 <- mean(((1-df_temp$TimeoutCalledInitially) * (df_temp$PossTeamWin - (predict(model_list[[i]][[2]], newdata=df_temp, type='prob')[,2]))/(1-predict(e_x, df_temp, type = "response"))) + (predict(model_list[[i]][[2]], newdata=df_temp, type='prob')[,2]))
  tau_aipws[[i]] <- (mu_hat_1 - mu_hat_0)
}
print(tau_aipws)
```
Next, we use the bootstrap to estimate the variance of our AIPW taus
```{r}
tau_boot1 <- list()
tau_boot2 <- list()
tau_boot3 <- list()
tau_boot4 <- list()
tau_boot5 <- list()
tau_boot6 <- list()
tau_boot <- list(tau_boot1, tau_boot2, tau_boot3, tau_boot4, tau_boot5, tau_boot6)
for (j in 1:1200){
    bootstrapped_df <- df_list[[(j%%6) + 1]][sample(nrow(df_list[[(j%%6) + 1]]), nrow(df_list[[(j%%6) + 1]]), replace = TRUE), ]
    
      model_1 <-  train(as.factor(PossTeamWin) ~ 1+StartPossTime+StartPossScoreDiff+StartTmPtsPerPoss
                 +HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute
                 +off_rating+def_rating,bootstrapped_df[bootstrapped_df$TimeoutCalledInitially==TRUE,], family = binomial, method = "rf", trControl = rfControl)
  
  model_0 <-  train(as.factor(PossTeamWin) ~ 1+StartPossTime+StartPossScoreDiff+StartTmPtsPerPoss
                 +HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute
                 +off_rating+def_rating, bootstrapped_df[bootstrapped_df$TimeoutCalledInitially==FALSE,], family = binomial, method = "rf", trControl = rfControl)
    
    mu_hat_1 <- mean((bootstrapped_df$TimeoutCalledInitially * (bootstrapped_df$PossTeamWin -predict(model_1, newdata=bootstrapped_df, type='prob')[,2])/predict(e_x, bootstrapped_df, type = "response")) + predict(model_1, newdata=bootstrapped_df, type='prob')[,2])
    
    mu_hat_0 <- mean(((1-bootstrapped_df$TimeoutCalledInitially) * (bootstrapped_df$PossTeamWin -predict(model_0, newdata=bootstrapped_df, type='prob')[,2])/(1-predict(e_x, bootstrapped_df, type = "response"))) + predict(model_0, newdata=bootstrapped_df, type='prob')[,2])
    tau_boot[[(j%%6) + 1]][[(as.integer(j/6)%%200) + 1]] <- (mu_hat_1 - mu_hat_0)
}
```

This gives us CIs for all of our taus for AIPW. Note that some of our intervals do not contain zero!
```{r}
for (i in 1:6) {
  alpha <- 0.05
  lower_bound <- sort(unlist(tau_boot[[i]]))[[5]]
  upper_bound <- sort(unlist(tau_boot[[i]]))[[195]]
  conf_interval <- c(lower_bound, upper_bound)
  print(conf_interval)
}

```


# Matched Pairs Design

```{r}
df1 <- df1 %>% 
  dplyr::mutate(StartEventBin = dplyr::case_when(
    StartEvent == "Drb" ~ "Drb",
    StartEvent == "Live Ball Turnover" ~ "Live",
    .default = "Dead"
  ))
```

Starting with full-data matching and working down towards forcing matches on the meta-variables. If that doesn't work, will look at matching within each combo-of-meta-variables subset.
```{r}
df1$propensity_hat <- predict(e_x, df1, type = "response")

ggplot(data = df1, aes(x = propensity_hat, 
                            group = TimeoutCalledInitially, 
                            fill = TimeoutCalledInitially)) + 
  geom_density(alpha = 0.5) + 
  theme_bw() + 
  labs(title = "Prop-hat densities, all obs", 
       x = "Est. propensity score", 
       y = "Density", 
       fill = "Group") + 
  scale_fill_discrete(name = "TO Called")

ggplot(data = subset(df1, TimeoutRemaining), 
       aes(x = propensity_hat, group = TimeoutCalledInitially, fill = TimeoutCalledInitially)) + 
  geom_density(alpha = 0.5) + 
  theme_bw() + 
  labs(title = "Prop-hat densities, with timeout remaining", 
       x = "Est. propensity score", 
       y = "Density", 
       fill = "Group") + 
  scale_fill_discrete(name = "TO Called")
```

Matching on mahalanobis distance with no caliper:
```{r}
match_formula <- formula(TimeoutCalledInitially ~ 
                                     StartEvent + StartPossTime + StartPossScoreDiff + 
                                     StartTmPtsPerPoss + HomePoss + IsPlayoffs + 
                                     SecondsSinceLastTimeout + ScoreDiffLastMinute + 
                                     off_rating + def_rating)

distance_matching_matrix <- optmatch::match_on(match_formula, 
                                   data = df1, 
                                   method = "mahalanobis",
                                   caliper = NULL)

distance_matching <- optmatch::pairmatch(distance_matching_matrix, data = df1)

plot(RItools::xBalance(match_formula, 
              strata = list(unstrat = NULL, distance_matching = ~ distance_matching), 
              data = df1), 
  ggplot = TRUE) +
  labs(title = "Changes in std. covariate differences, no caliper", 
       x = "Standardized difference, no-caliper matching", 
       y = "Variable")

sum(!is.na(distance_matching)) / 2 # number of pairs
```

```{r}
avg_and_max_e_hat_diffs <- function(data, pairs_var) {
  # given a data frame and a pairing variable containing matches, 
  # print average and max absolute differences in propensity scores across pairs
  
  grouped <- data %>% 
    dplyr::filter(!is.na({{pairs_var}})) %>% # keep only matched observations
    dplyr::group_by({{pairs_var}}) %>% # group by pair
    dplyr::summarise(smaller_pair_est_prop_score = min(propensity_hat), 
                     larger_pair_est_prop_score = max(propensity_hat), 
                     abs_diff_est_prop_score = 
                       larger_pair_est_prop_score - smaller_pair_est_prop_score)

  mean_absdiff_i <- mean(grouped$abs_diff_est_prop_score)
  print(paste0("The average absolute difference in estimated propensity scores ",
               "within matched pairs is ", round(mean_absdiff_i, 4), "."))
  
  max_absdiff_i <- max(grouped$abs_diff_est_prop_score)
  print(paste0("The maximum absolute difference in estimated propensity scores ",
               "within matched pairs is ", round(max_absdiff_i, 4), "."))
}

df1$no_caliper_pair <- as.character(distance_matching)
avg_and_max_e_hat_diffs(df1, no_caliper_pair)
```

Caliper matching:
```{r}
caliper_matching_matrix <- DOS2::addcaliper(distance_matching_matrix, 
                                   z = df1$TimeoutCalledInitially, 
                                   p = df1$propensity_hat, 
                                   caliper = .1)

caliper_matching <- optmatch::pairmatch(caliper_matching_matrix, data = df1)

plot(RItools::xBalance(match_formula, 
              strata = list(unstrat = NULL, caliper_matching = ~ caliper_matching), 
              data = df1), 
  ggplot = TRUE) +
  labs(title = "Changes in std. covariate differences, caliper", 
       x = "Standardized difference, caliper matching", 
       y = "Variable")

df1$caliper_pair <- as.character(caliper_matching)
avg_and_max_e_hat_diffs(df1, caliper_pair)
```

```{r}
force_match_time_and_start_matrix <- DOS2::addalmostexact(caliper_matching_matrix, 
  z = df1$TimeoutCalledInitially, f = df1$TimeBins, mult = 5) %>% 
  DOS2::addalmostexact(z = df1$TimeoutCalledInitially, f = df1$StartEventBin, mult = 5)

force_time_and_start_matches <- optmatch::pairmatch(force_match_time_and_start_matrix, 
                                         data = df1, 
                                         remove.unmatchables = TRUE)

match_formula_with_forcing_vars <- formula(TimeoutCalledInitially ~ 
                                     StartEvent + StartPossTime + StartPossScoreDiff + 
                                     StartTmPtsPerPoss + HomePoss + IsPlayoffs + 
                                     SecondsSinceLastTimeout + ScoreDiffLastMinute + 
                                     off_rating + def_rating + TimeBins + StartEventBin)

plot(RItools::xBalance(match_formula_with_forcing_vars, 
              strata = list(unstrat = NULL, 
                force_time_and_start_matches = ~ force_time_and_start_matches), 
              data = df1), 
  ggplot = TRUE) +
  labs(title = "Std. cov. diffs., caliper, force-matched", 
       x = "Std. diff., caliper force-matching", 
       y = "Variable")
```

Even with DOS2::addalmostexact, we don't get exact matches on the time bin and the event start type (standardized differences not exactly 0). Assuming our results will always be stratified by those groups (and we're not interested in an overall tau-hat), exact matching would be preferable. As a result, looking at subsetting the data into those six subsets, then matching within each:
```{r}
match_formula_subset <- formula(TimeoutCalledInitially ~ 
                                     StartPossTime + StartPossScoreDiff + 
                                     StartTmPtsPerPoss + HomePoss + IsPlayoffs + 
                                     SecondsSinceLastTimeout + ScoreDiffLastMinute + 
                                     off_rating + def_rating)

par(mfrow = c(3, 2))
for (i in 1:6) {
  grp <- names(df_list)[i]
  df_subset <- df_list[[i]]
  df_subset$propensity_hat <- predict(e_x, df_subset, type = "response")
  
  distance_matching_matrix_subset <- optmatch::match_on(match_formula_subset, 
                                   data = df_subset, 
                                   method = "mahalanobis",
                                   caliper = NULL)

  distance_matching_subset <- optmatch::pairmatch(distance_matching_matrix_subset, data = df_subset)
  
  print(plot(RItools::xBalance(match_formula_subset, 
                strata = list(unstrat = NULL, distance_matching_subset = ~ distance_matching_subset), 
                data = df_subset), 
    ggplot = TRUE) +
    labs(title = paste0(grp, " -- no caliper"), 
         x = "Standardized difference, no-caliper matching", 
         y = "Variable"))
  
  print(paste0("Number of matches, ", grp, ": ", sum(!is.na(distance_matching_subset)) / 2))
  df_subset$no_caliper_pair <- as.character(distance_matching_subset)
  avg_and_max_e_hat_diffs(df_subset, no_caliper_pair)
}
```

Not ideal. If we add a caliper and focus on propensity-score matching, do the covariates wind up being close enough for the interpretability of matching as a process to still be a major benefit in our case?
```{r}
for (i in 1:6) {
  grp <- names(df_list)[i]
  df_subset <- df_list[[i]]
  df_subset$propensity_hat <- predict(e_x, df_subset, type = "response")
  
  distance_matching_matrix_subset <- optmatch::match_on(match_formula_subset, 
                                   data = df_subset, 
                                   method = "mahalanobis",
                                   caliper = NULL)

  caliper_matching_matrix_subset <- DOS2::addcaliper(distance_matching_matrix_subset, 
                                     z = df_subset$TimeoutCalledInitially, 
                                     p = df_subset$propensity_hat, 
                                     caliper = .05)
  
  caliper_matching_subset <- optmatch::pairmatch(caliper_matching_matrix_subset, data = df_subset)
  
  print(plot(RItools::xBalance(match_formula_subset, 
                strata = list(unstrat = NULL, caliper_matching_subset = ~ caliper_matching_subset), 
                data = df_subset), 
    ggplot = TRUE) +
    labs(title = paste0(grp, " -- caliper"), 
         x = "Standardized difference, caliper matching", 
         y = "Variable"))
  
  print(paste0(grp, ", caliper-matching details:"))
  print(paste0("Number of matches, ", grp, ": ", sum(!is.na(caliper_matching_subset)) / 2))
  df_subset$caliper_pair <- as.character(caliper_matching_subset)
  avg_and_max_e_hat_diffs(df_subset, caliper_pair)
    
  # FRT analysis for p-value
  df_subset$pair <- as.numeric(caliper_matching_subset)
  df_subset_2 <- df_subset %>% 
    dplyr::filter(!is.na(pair)) %>% 
    dplyr::group_by(pair) %>% 
    dplyr::summarise(y_control = c(PossTeamWin[which(TimeoutCalledInitially == 0)]), 
                     y_treatment = c(PossTeamWin[which(TimeoutCalledInitially == 1)]))
  
  n_pairs <- nrow(df_subset_2)
  tau_hat <- sum(df_subset_2$y_treatment - df_subset_2$y_control) / n_pairs
  
  set.seed(0)
  total_runs <- 20000
  tau_hats_FRT <- rep(NA, total_runs)
  for (j in 1:total_runs) {
    data_run <- df_subset_2
    data_run$swap <- rbinom(n = n_pairs, size = 1, prob = .5)
    
    data_run$y_control <- df_subset_2$y_control * (1 - data_run$swap) + 
      df_subset_2$y_treatment * data_run$swap
    
    data_run$y_treatment <- df_subset_2$y_treatment * (1 - data_run$swap) + 
      df_subset_2$y_control * data_run$swap
    
    pi_k <- 1 / n_pairs # true for all "strata," since each straum is a pair
    tau_hats_FRT[j] <-  sum(pi_k * (data_run$y_treatment - data_run$y_control))
  }
  
  print(paste0("Tau-hat-matching: ", round(tau_hat, 4)))
  if (tau_hat < 0) {
    p_val_subset <- sum(tau_hats_FRT < tau_hat) / length(tau_hats_FRT)
  } else {
    p_val_subset <- sum(tau_hats_FRT > tau_hat) / length(tau_hats_FRT)
  }
  print(paste0("P-value from the FRT: ", round(p_val_subset, 4)))
  
  print("-----")
}
```

Ehh. Not too excited about it. And even when using one-sided FRTs, we'd only reject for the first group, which has the largest absolute "matching" tau-hat. (Four out of the six confidence intervals from AIPW didn't include 0.)

Going back to full-data matching and trying to force on the meta-variables (might wind up being the same matches, but the full-data picture on the covariates makes for a better story, if we can get the meta-variables right):

```{r}
force_match_time_and_start_matrix <- DOS2::addalmostexact(caliper_matching_matrix, 
  z = df1$TimeoutCalledInitially, f = df1$TimeBins, mult = 6) %>% 
  DOS2::addalmostexact(z = df1$TimeoutCalledInitially, f = df1$StartEventBin, mult = 6)
```

In our case, if mult is over 5 (leading to a total mult over 25 for some obs), optmatch::pairmatch doesn't converge. Overall takeaway -- we can use matching if we want, but the covariate balances aren't ideal from an interpretability standpoint (despite the mathematical thumbs-up of pretty good propensity-score matching).

One more code chunk: for plotting treatment incidence rates given a timeout available (as discussed in the "discussion" section).

```{r}
rates <- rep(NA, 6)
names(rates) <- c("3-8, LB", "3-8, DRB", "3-8, DB", 
                  "8-24, LB", "8-24, DRB", "8-24, DB")
for (i in 1:6) {
  to_avail <- df_list[[i]] %>% 
    dplyr::filter(TimeoutRemaining)
  rates[i] <- sum(to_avail$TimeoutCalledInitially)/nrow(to_avail)
}
rates <- rates * 100
rates_df <- data.frame(Group = names(rates), TO_Incidence = rates)

ggplot(data = rates_df, 
       aes(x = Group, y = TO_Incidence, fill = as.factor(Group))) + 
  geom_bar(stat = "identity") + 
  scale_fill_brewer() +
  theme(legend.position = "none", panel.background = element_blank()) + 
  scale_y_continuous("Timeout Incidence (%)") + 
  ggtitle("% TO called given TO remaining, by scenario")
```
