---
title: "Causal_analysis"
author: "Johannes Fuest"
date: "12/2/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read data and add correct defensive rating to df
```{r outcome regression}
df1 <- read.csv('data_with_to_info.csv')
names(df1)[names(df1) == "def_rating"] <- "def_rating_old"
names(df1)[names(df1) == "TimeBins"] <- "TimeBins_old"
df2 <- read.csv('poss_summary.csv')
df1 <- merge(df1, df2[c("GameID", "def_rating", "Possession", "TimeBins")], by = c("GameID", "Possession"), all.x = TRUE)
df1$def_rating_old <- NULL
df1$TimeBins_old <- NULL
#TO DO: unsure what this column is and why 33% of its values are null -> ask the squad
df1$HomeTeamTimeout <- NULL
df1 <- na.omit(df1)
columns_to_keep <- c("StartPossScoreDiff","TimeBins","PossTeamWin","TimeoutCalledInitially","StartPossTime","StartTmScore","StartOppScore","StartTmPtsPerPoss","StartOppPtsPerPoss","HomePoss","IsPlayoffs","StartEvent","SecondsSinceLastTimeout","ScoreDiffLastMinute","TimeoutTime", "Period", "off_rating", "TimeoutRemaining", "def_rating")
df1 <- df1[,columns_to_keep]
df1$Period <- as.factor(df1$Period)
```

First up, we look at the basic diff-in-means:
```{r}
print(mean(df1[df1$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df1[df1$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
```
Calling a timeout appears to have a marginally positive effect, but there is 
only a .3% difference in means. It looks like not much is going on. 

Next, we split up by bins of seconds left, which is known to make an enormous 
difference and repeat our calculation.
```{r}
df_0to6 <- df1[df1$TimeBins == '[0,6]',]
df_6to12 <- df1[df1$TimeBins == '(6,12]',]
df_12to24 <- df1[(df1$TimeBins != '[0,6]' & df1$TimeBins != '(6,12]'),]
print(mean(df_0to6[df_0to6$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_0to6[df_0to6$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_6to12[df_6to12$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_6to12[df_6to12$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_12to24[df_12to24$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_12to24[df_12to24$TimeoutCalledInitially == FALSE, ]$PossTeamWin))

```
Here we can already see that the effect can change direction based on seconds left

Next, we split up by bins of seconds left, which is known to make an enormous 
difference and repeat our calculation.

```{r}
df_0to6_live <- df_0to6[df_0to6$StartEvent == "Live Ball Turnover",]
df_0to6_drb <- df_0to6[df_0to6$StartEvent == "Drb",]
df_0to6_dead <- df_0to6[df_0to6$StartEvent != "Live Ball Turnover" & df_0to6$StartEvent != "Drb" ,]
df_6to12_live <- df_6to12[df_6to12$StartEvent == "Live Ball Turnover",]
df_6to12_drb <- df_6to12[df_6to12$StartEvent == "Drb",]
df_6to12_dead <- df_6to12[df_6to12$StartEvent != "Live Ball Turnover" & df_6to12$StartEvent != "Drb" ,]
df_12to24_live <- df_12to24[df_12to24$StartEvent == "Live Ball Turnover",]
df_12to24_drb <- df_12to24[df_12to24$StartEvent == "Drb",]
df_12to24_dead <- df_12to24[df_12to24$StartEvent != "Live Ball Turnover" & df_12to24$StartEvent != "Drb" ,]

print(mean(df_0to6_live[df_0to6_live$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_0to6_live[df_0to6_live$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_0to6_drb[df_0to6_drb$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_0to6_drb[df_0to6_drb$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_0to6[df_0to6$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_0to6[df_0to6$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_6to12_live[df_6to12_live$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_6to12_live[df_6to12_live$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_6to12_drb[df_6to12_drb$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_6to12_drb[df_6to12_drb$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_6to12[df_6to12$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_6to12[df_6to12$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_12to24_live[df_12to24_live$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_12to24_live[df_12to24_live$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_12to24_drb[df_12to24_drb$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_12to24_drb[df_12to24_drb$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
print(mean(df_12to24_dead[df_12to24_dead$TimeoutCalledInitially == TRUE, ]$PossTeamWin) - mean(df_12to24_dead[df_12to24_dead$TimeoutCalledInitially == FALSE, ]$PossTeamWin))
```
With the exception of possessions with more than 12 seconds remaining, we see that
the sign of diff-in-means changes depending on event. With these meta_variables 
in place, we can now begin estimating the true treatment effect of the timeout
call holding constant our covariates. We will do this by using AIPW:

1.) Esimate propensity scores using logistic regression. We will keep meta
variables in model. #TODO: ask Dominik/TAs if this is fine (bias?) We also do not
use Timeoutremaining here
```{r}
df_timeouts <- df1[df1$TimeoutRemaining == TRUE,]
# not using starting scores and per minute scores to avoid multicollinearity (was getting N/A coef values)
e_x <- glm(TimeoutCalledInitially ~ 1+StartPossScoreDiff+StartPossTime+StartTmPtsPerPoss+
               StartOppPtsPerPoss+HomePoss+IsPlayoffs+StartEvent+SecondsSinceLastTimeout+ScoreDiffLastMinute+off_rating+def_rating,
             data = df_timeouts, family = binomial)
summary(e_x)
```
2.) Estimate outcome variable with logistic regression for each df
```{r}
# missing
df_list <- list(df_0to6_live,df_0to6_drb, df_0to6_dead, df_6to12_live, df_6to12_drb, df_6to12_dead, df_12to24_live, df_12to24_drb, df_12to24_dead)
model_list <- list()

# Loop through each DataFrame and fit a logistic regression model on treatments and controls respectively (have to leave out starting event, also leaving out period due to issues from rare overtimes)
for (i in 1:length(df_list)) {
  
  model_1 <- glm(PossTeamWin ~ 1+TimeoutCalledInitially+StartPossScoreDiff+StartPossTime+StartTmPtsPerPoss+
               StartOppPtsPerPoss+HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute+off_rating+def_rating,
             data = df_list[[i]][df_list[[i]]$TimeoutCalledInitially==TRUE,], family = binomial)
  model_0 <- glm(PossTeamWin ~ 1+TimeoutCalledInitially+StartPossScoreDiff+StartPossTime+StartTmPtsPerPoss+
               StartOppPtsPerPoss+HomePoss+IsPlayoffs+SecondsSinceLastTimeout+ScoreDiffLastMinute+off_rating+def_rating,
             data = df_list[[i]][df_list[[i]]$TimeoutCalledInitially==FALSE,], family = binomial)
  model_list[[i]] <- list(model_1, model_0)
}
```
3.) Estimate $$\hat{\mu}^{adj}$$
```{r}
tau_aipws <- list()
for (i in 1:length(df_list)) {
  print(i)
  df_temp <- df_list[[i]]
  mu_hat_1 <- mean((df_temp$TimeoutCalledInitially * (df_temp$PossTeamWin - predict(model_list[[i]][[1]], df_temp, type = "response"))/predict(e_x, df_temp, type = "response")) +  predict(model_list[[i]][[1]], df_temp, type = "response"))
  mu_hat_0 <- mean((df_temp$TimeoutCalledInitially * (df_temp$PossTeamWin - predict(model_list[[i]][[2]], df_temp, type = "response"))/predict(e_x, df_temp, type = "response")) +  predict(model_list[[i]][[2]], df_temp, type = "response"))
  tau_aipws[[i]] <- (mu_hat_1 - mu_hat_0)
}
print(tau_aipws)
```
#TO DO: discuss numbers with team, bootstrapping
```{r}

```


