---
title: "team_stats"
author: "Johannes Fuest"
date: "12/3/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(zoo)
team_box <- load_nba_team_box(seasons = seq(2010,2022))
```

```{r}
# join to get number of possessions
team_box <- left_join(team_box, df, by = c("game_id" = "ESPNGameID"))
```{r}
final_df <- team_box %>%
  arrange(season, team_name, game_date) %>%
  group_by(season, team_name) %>%
  mutate(
    off_rating = rollapply(team_score / (Possession / 2), width = 11, FUN = function(x) mean(head(x, -1), na.rm = TRUE), partial = TRUE, fill = NA, align = "right"),
    def_rating = rollapply(opponent_team_score/ (Possession / 2), width = 11, FUN = function(x) mean(head(x, -1), na.rm = TRUE), partial = TRUE, fill = NA, align = "right")
  ) %>%
  select(season, team_name, game_date, team_score, opponent_team_score, off_rating, def_rating, season_type, Possession)
```

```{r}
# replace playoff score with most recent regular season score
final_df <- final_df %>%
  arrange(season, team_name, game_date) %>%  # Ensure the data is ordered
  group_by(season, team_name) %>%
  mutate(
    last_rating = ifelse(season_type == 2, off_rating, NA),  # Mark the rating for season_type = 2
    last_rating = zoo::na.locf(last_rating, na.rm = FALSE),       # Carry the last non-NA forward
    off_rating = ifelse(season_type == 3, last_rating, off_rating)  # Replace if season_type is 3
  )